% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%Section: Work Experience at the top
\sectionTitle{Expérience Professionelle}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \experience
    {Nielsen}   {MROI | Product Development and Innovation}{AAC}{Bangalore, India}
    {May,17 - Present} {
                      \begin{itemize}
                        \item Development of Marketing Mix Modeling and Market Planner tool using Python based on Hierarchical Linear Model (HLM), Generalized reduced gradient decent (GRG2) and Monte Carlo Simulation. 
                        \item Profiling and Optimizing code using SnakeViz, profvis, Rcpp, Numba, Cython and Dask.
                        \item In depth understanding of additive and multiplicative model in Marketing Research Domain.
                        \item Monitoring and maintenance of staging and production server.
                        \item Extensively used Non-Linear box constraint based optimization (gradient and non-gradient based methods) with help of various python and R libraries.
                        \item Vendor management and continuous communication with user community.
                        \item Developing methodology related documents for internal and external communication.
                        \end{itemize}
                    }
                    {Python, Flask, Numpy, Pandas, Postman, Jenkins, R, tidyverse, docker, CentOS}
  \emptySeparator
  \experience
    {Chegg, Inc.} {Subject matter expert}{Statistics}{Data Science}
    {Jan, 16 - May, 17}    {
                      \begin{itemize}
                        \item Teaching graduate and under-graduate students statistics, mathematics and economics.                           
                        \item Helping with academic assignments in MLA, APA and other academic formats.                       
                        \item Helping students writing research paper and proposal for journal and conferences.  
                        \item Developing reading materials, solving text book based problems and various concepts related to statistics and computer science with graphical illustrations.   
                        \item Designed multiple online tests, assignments and programming assignment tests using shiny server pro including user authentication.  
                      \end{itemize}
                    }
                    {Tutorial, Academic Writing, Research Methodology, Statistics Tutor}
  
  \emptySeparator
  \experience
    {Blue Copper}{Business Analyst (Intern) , Blue Copper Technologies}{Calcutta}{India}
    {Jnue - August, 16}    {
                      \begin{itemize}
                        \item Developing predictive models, information extraction and visualization from web using interactive dashboard solution.
                        \item Predictive model building (linear regression, logistic regression) and residual diagnostics using graphical methods. Extensively used ggplot2 and shiny to build interactive dash-boarding solution.
                        
                        \item Basic text processing, cleaning, stemming, corpus formation, association mining, term document matrix and TF-IDF construction in R. 
                        
                        \item Used Named Entity Recognition using Max Entropy classifier. Developed Latent Dirichlet Allocation and Correlated Topic Model based topic models.       
                        
                        \item Applied shallow neural network based models such as Word2Vec and Doc2Vec, N-grams, Skip-grams, tidytext and lexicon based methodologies for sentiment and polarity analysis using R. Extensively used NLP, OpenNLP, tm, tidytext and  syuzhet package for textual analysis.                
                      \end{itemize}
                    }
                    {R, htmlwidget, Word2Vec,Doc2Vec, shiny, Regression, NLP, Web Scraping, NER, MaxEnt, Sentiment Analysis}
\end{experiences}
